---
title: "BEF Bayesian Workflow"
output:
  github_document:
    toc: true
    toc_depth: 3
    html_preview: false
    df_print: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 9,
  fig.height = 6
)
script_dir <- dirname(knitr::current_input(dir = TRUE))
project_root <- normalizePath(file.path(script_dir, ".."), mustWork = TRUE)
setwd(script_dir)

wf <- new.env(parent = globalenv())
source(file.path(script_dir, "02_developing_BEF_Allometrics_Bayes.R"), local = wf)
```

# Overview

This report is generated from the workflow script [02_developing_BEF_Allometrics_Bayes.R](02_developing_BEF_Allometrics_Bayes.R).  
Edit the `.R` file only. The Markdown file is a GitHub-readable record of that run.

```{r overview}
cat("**Run ID:**", wf$run_id, "\n\n")
cat("**Run time:**", wf$run_generated_at, "\n\n")
cat("**Project root:**", project_root, "\n\n")
cat("**Output directory:**", wf$out_dir, "\n\n")
```

# Inputs

```{r inputs}
input_manifest <- wf$manifest
input_manifest$model_time <- format(as.POSIXct(input_manifest$model_time), "%Y-%m-%d %H:%M:%S")

knitr::kable(
  input_manifest[, c("model", "model_file", "model_time", "n_rows")],
  col.names = c("Model", "File", "File time", "Rows"),
  align = c("l", "l", "l", "r")
)
```

# Diagnostics

```{r diagnostics}
diag_tbl <- wf$step1[, c(
  "model", "divergences", "max_treedepth", "max_rhat",
  "max_rhat_parameter", "min_bulk_ess", "min_bulk_ess_parameter",
  "min_tail_ess", "min_tail_ess_parameter"
)]

knitr::kable(
  diag_tbl,
  digits = 3,
  align = c("l", "r", "r", "r", "l", "r", "l", "r", "l")
)
```

# Posterior Summaries

```{r posterior-summaries}
post_tbl <- wf$step2
post_tbl <- post_tbl[post_tbl$variable %in% c(
  "b_y1m1_logL_Intercept", "b_y1m1_logA_Intercept", "b_y1m1_logk_Intercept",
  "b_y2_logL_Intercept", "b_y2_logA_Intercept", "b_y2_logk_Intercept",
  "sd_h1__y1m1_logL_Intercept", "sd_h1__y1m1_logA_Intercept",
  "sd_h1__y2_logL_Intercept", "sd_h1__y2_logA_Intercept"
), ]

knitr::kable(
  post_tbl[, c("model", "variable", "mean", "median", "sd", "q5", "q95")],
  digits = 4,
  align = c("l", "l", "r", "r", "r", "r", "r")
)
```

# Posterior Predictive Checks

The next table compares observed values with posterior predictive draws on the original scale.

```{r ppcheck-summary}
pp_tbl <- wf$step3_summary
knitr::kable(
  pp_tbl[, c(
    "model", "response", "n", "observed_mean", "yrep_median_mean",
    "mean_residual", "rmse", "mean_abs_std_residual",
    "prop_outside_yrep90", "prop_pp_twotail_lt_0.10", "prop_pp_twotail_lt_0.05"
  )],
  digits = 4,
  align = c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r")
)
```

# Model Comparison

```{r loo-ranking}
loo_tbl <- wf$step5_total
knitr::kable(
  loo_tbl[, c(
    "model", "elpd_loo", "p_loo", "looic", "max_pareto_k",
    "n_pareto_k_gt_0.7", "n_pareto_k_gt_1.0", "elpd_diff_from_best",
    "looic_diff_from_best"
  )],
  digits = 3,
  align = c("l", "r", "r", "r", "r", "r", "r", "r", "r")
)
```

# Outputs

```{r outputs}
out_files <- sort(list.files(wf$out_dir))
out_tbl <- data.frame(
  file = out_files,
  path = file.path(wf$out_dir, out_files),
  stringsAsFactors = FALSE
)

knitr::kable(
  out_tbl,
  col.names = c("File", "Path"),
  escape = FALSE,
  align = c("l", "l")
)
```

# Reproducibility

```{r reproducibility}
cat("**R version:**", R.version.string, "\n\n")
cat("**Loaded packages:** `brms`, `posterior`, `loo`\n\n")
cat("**Project root:**", project_root, "\n\n")
cat("**Workflow script:**", file.path(script_dir, "02_developing_BEF_Allometrics_Bayes.R"), "\n\n")
```

```{r session-info, results='asis'}
cat("```text\n")
cat(paste(capture.output(sessionInfo()), collapse = "\n"))
cat("\n```\n")
```

<details>
<summary>Workflow script</summary>

```{r workflow-script, echo=FALSE, results='asis'}
cat("```r\n")
cat(readLines(file.path(script_dir, "02_developing_BEF_Allometrics_Bayes.R")), sep = "\n")
cat("\n```\n")
```

</details>
